Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying

### 2023-02-21 Outputs/Paper/paper.qmd
update paper 4

You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.

talking points 1) why asian population? because anti-asian violence in the usa grew. we want to see if anti-asian violence was also reflected in school and cyber bullying (introduction). (will)

2)  our replicated graphs show that bullying numbers dropped during covid, (wil)

3)  But there wasnt a significant correlation between asian population of states and school bullying numbers (annie)

4)  do a comparison of top 10 asian vs bottom 10 asian population states to see if asian population actually matters in school bullying (jason)

5)  lack of correlation testing, this is only reported bullying, not reflected of everyone getting bullied. only those that search (annie)

6)  next steps: try asian population in certain schools instead of states? a hard comparison between asian bullying and violence? (annie)

7)  bias of only reported data (sampling) with people that only searches for bullying. ethics of using peoples search data. unreliability of measurement. not every1 uses google for searches or bullying help. google's algorithm will shift towards anti-bullying stuff for people that search for it. (will)

@@

```{r}
#| label: bullydata
#| fig-cap: 3 graphs lol
#| echo: false
#| warning: false

sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "All 'Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'Cyberbullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'School Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

@@

### bullying number droped after covid

@@

Anti-Asian violence skyrocketed over the pandemic. The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before. The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles. The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60. American culture pretends Asian Americans face no discrimination or racism. There are countless examples where when the U.S. was faced with an economic downturn, Asian Americans were affected. The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873. It's safe to assume an economic horror like the pandemic would lead to hate. It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs. From the data provided, we decided to clean it, focusing on the states with an Asian population. There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth. (could be apart of introduction)

@@

### compare top 10 and bottom 10

@@

# Discussion
## First discussion point

@@

## Third discussion point

@@

>>>>

Anti-Asian violence skyrocketed over the pandemic. The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before. The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles. The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60. American culture pretends Asian Americans face no discrimination or racism. There are countless examples where when the U.S. was faced with an economic downturn, Asian Americans were affected. The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873. It's safe to assume an economic horror like the pandemic would lead to hate. It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs. From the data provided, we decided to clean it, focusing on the states with an Asian population. There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth.

@@

@@

### Bullying search droped after COVID-19

```{r}
#| label: All Bullying Searches in High Asian Population States
#| fig-cap: All Bullying Searches in High Asian Population States
#| echo: false
#| warning: false

sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "All 'Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )
```

```{r}
#| label: Cyberbullying Searches in High Asian Population States
#| fig-cap: Cyberbullying Searches in High Asian Population States
#| echo: false
#| warning: false
library(tidyverse)
sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'Cyberbullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )
```

```{r}
#| label: School Bullying Searches in High Asian Population States
#| fig-cap: School Bullying Searches in High Asian Population States
#| echo: false
#| warning: false
library(tidyverse)
sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'School Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

@@

@@

### Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population

@@

# Discussion
## Bullying search relate to COVID-19

@@

## Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population

@@

\newpage
